---
title: "esm 206 lab 7"
author: "Logan Babcock"
date: "November 8, 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

# attach packages
library(tidyverse)
library(palmerpenguins)
library(GGally)
library(broom)
library(kableExtra)
library(modelsummary)


```

## Intro to ggpairs
Use GGaly::ggpairs() function to create a pairs plot
```{r}
ggpairs(penguins) # makes a big overview plot of everything compared against eachother


```

```{r}
# makign a new dataset
penguins %>%
  select(species, bill_length_mm:body_mass_g) %>%  # selects species columns and all between the length and body mass 
  ggpairs(aes(color = species))

# exporing tha relationship more
ggplot(data = penguins, aes(x = bill_depth_mm, y = body_mass_g, group = species)) +
  geom_point(aes(color = species)) +
  geom_smooth(method = "lm", aes(color = species))



```

## Multiple linear regression - penguins

Use mutiple linear regression to try and understand the relationship between mutiple predictor variables and a single continuous outcome variable (body mass). 
```{r}
# model naming and creation

penguin_lm <-lm(body_mass_g ~ flipper_length_mm + bill_depth_mm, data = penguins) # writing in function notation

# return just the coefficients: 
penguin_lm
```

How would we interpret this?
on average, we would expect a 1 mm increase in flippper length to be associated with a ` r penguin_lm$coef[2]` increase in body mass, if everything else is constant.

