---
title: "esm 206 lab 7"
author: "Logan Babcock"
date: "November 8, 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

# attach packages
library(tidyverse)
library(palmerpenguins)
library(GGally)
library(broom)
library(kableExtra)
library(modelsummary)
library(stargazer)



```

## Intro to ggpairs
Use GGaly::ggpairs() function to create a pairs plot
```{r}
ggpairs(penguins) # makes a big overview plot of everything compared against eachother


```

```{r}
# makign a new dataset
penguins %>%
  select(species, bill_length_mm:body_mass_g) %>%  # selects species columns and all between the length and body mass 
  ggpairs(aes(color = species))

# exporing tha relationship more
ggplot(data = penguins, aes(x = bill_depth_mm, y = body_mass_g, group = species)) +
  geom_point(aes(color = species)) +
  geom_smooth(method = "lm", aes(color = species))



```

## Multiple linear regression - penguins

Use mutiple linear regression to try and understand the relationship between mutiple predictor variables and a single continuous outcome variable (body mass). 
```{r}
# model naming and creation

penguin_lm <-lm(body_mass_g ~ flipper_length_mm + bill_depth_mm, data = penguins) # writing in function notation

# return just the coefficients: 
penguin_lm
```

How would we interpret this?
on average, we would expect a 1 mm increase in flippper length to be associated with a 54.51 increase in body mass, if everything else is constant.

```{r}
summary(penguin_lm)

```
r squared analysis: ' 75% of the variance in bodymass can be expained by the variables in this model. 

### Use broom functions tidy and glance

use broom::tidy to get the coef summary in a dataframe
use broom::glance to et the model summary in a dataframe

```{r}
penguins_lm_tidy <- tidy(penguin_lm)
penguins_lm_glance <- glance(penguin_lm)

# view tidy set
penguins_lm_tidy

```

Using in line code to pull bill depth coeficient
the bill depth coefficient: `r penguins_lm_tidy$estimate[3]`

```{r}
# view penguin glance table 
penguins_lm_glance

```
## try abother model! 

We have thought really hard, done a literature review, consulted experts, and decided that the three most critical variables to include in this model are 

- flipper length
- species
- sex

# create a mutiple linear regression model using these three predictor variables for body mass
```{r}
# mutiple variable linear model
penguins_lm_2 <- lm(body_mass_g ~ flipper_length_mm + species + sex, data = penguins)

# return coefficients
penguins_lm_2
```

Adele species are the reference species, and female is the reference sex, becuase they do not show up in the coefficients output. 

coefficient output written out:
mass(g) = -365.82 = 20.02(flipper length) - 87.63(chinstrap) + 836.26(Gentoo) + 530.38(male)

 make sure to reference the reference level in interpretation!!!! 
  - "If all other conditions were the same, we would expect a gentoo penguin to be on average for the bodymass of a gentoo penguin to be 836.26 grams more than an adele penguin"

## use broom::augment to see predicted values
```{r}
augment(penguins_lm_2)

```
## using plot to see residuals (model diagnostics)
```{r}
plot(penguins_lm_2)

```
-conceptual understanding and expertise allows me to resposible determine that penguin species, sex, and flipper length are reasonable predictor variables. 
- diagnostis plots check out for normality of residuals, homscedasticity, and no worrisome outliers (<<< last one is not an assumption!)


## Make output tabels
```{r}
modelsummary(penguins_lm_2)
```
Using stargazer:
```{r, results = "asis"}
stargazer(penguins_lm_2, type = "html")

```

